Example Manuscript Template for a Data Analysis Project

### 2024-07-26 products/manuscript/Manuscript.qmd
Updated Readme and manuscript file

The structure below is one possible setup for a data analysis project (including the course project). For a manuscript, adjust as needed. 
You don't need to have exactly these sections, but the content covering those sections should be addressed.

This uses MS Word as output format. [See here](https://quarto.org/docs/output-formats/ms-word.html) for more information. You can switch to other formats, like html or pdf. See [the Quarto documentation](https://quarto.org/) for other formats.

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
```

-   https://www.google.com/publicdata/directory
-   https://www.data.gov/
-   https://github.com/awesomedata/awesome-public-datasets
-   https://registry.opendata.aws/
-   https://www.kaggle.com/datasets

- https://www.kaggle.com/datasets/jainaru/electric-vehicle-population

@@

The dataset obtained from Kaggle provides detailed information about Battery Electric Vehicles (BEVs) and Plug-in Hybrid Electric Vehicles (PHEVs) registered through the Washington State Department of Licensing (DOL). It comprises 181,458 observations and 17 variables, encompassing key details such as Vehicle Identification Number (VIN), county, city, model year, electric range, and more.

@@

**- (a) Briefly describe what the data is, how it was collected, where you will get (or got) it from. How many observations do you have, what was measured? Anything else important to report about the data?**

The dataset obtained from Kaggle provides detailed information about Battery Electric Vehicles (BEVs) and Plug-in Hybrid Electric Vehicles (PHEVs) registered through the Washington State Department of Licensing (DOL). It comprises 181,458 observations and 17 variables, encompassing key details such as Vehicle Identification Number (VIN), county, city, model year, electric range, and more.

**- (b) At this stage you are not required to already have and show the data, but if you do, even better. Then add a few lines of code which load the data and using some of the commands you learned about, provide summary descriptions of the data.**
```{r}
data_location <- here::here("data","raw-data","Electric_Vehicle_Population_Data.csv")
data <- read.csv(data_location)
str(data)
head(data)
summary(data)
colSums(is.na(data))
```

>>>>

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
```
Data Sources for the work:

-   https://www.google.com/publicdata/directory
-   https://www.data.gov/
-   https://github.com/awesomedata/awesome-public-datasets
-   https://registry.opendata.aws/
-   https://www.kaggle.com/datasets/jainaru/electric-vehicle-population

@@

Electric vehicle market penetration is an important topic of interest for a variety of government agencies and automotive companies in terms of planning future charging infrastructure and inventory management. This project aims to aid this process by creation of a data driven model that can predict the number of electric vehicles in a given zip code based on a variety of factors. The data used in this project was sourced from the Washington State Department of Licensing (DOL) and includes information on Battery Electric Vehicles (BEVs) and Plug-in Hybrid Electric Vehicles (PHEVs) registered in Washington State. The data set contains 181,458 observations and 17 variables, including Vehicle Identification Number (VIN), county, city, model year, electric range, and more. The project will involve data cleaning, exploratory data analysis, and statistical modeling to identify key factors influencing electric vehicle adoption and predict the number of electric vehicles in a given zip code. The results of this project will provide valuable insights for policymakers, urban planners, and automotive companies to support the transition to sustainable transportation.

@@

The dataset obtained from Kaggle provides detailed information about Battery Electric Vehicles (BEVs) and Plug-in Hybrid Electric Vehicles (PHEVs) registered through the Washington State Department of Licensing (DOL). It comprises 181,458 observations and 17 variables, encompassing key details such as Vehicle Identification Number (VIN), county, city, model year, electric range, and more.This document is an exploratory data analysis of electric vehicle data.

A second set of data was obtained from the IRS and contains information on electric vehicles, their owners, and the tax benefits they receive. The data was cleaned and processed in R and saved as a CSV file.  This data was then combined with thwe data from kaggle to conduct the analysis of data and model creation that predicts number of electric vehicles in a given zip code based on various input varaibles.

# Data set Analysis 
```{r}
data_location <- here::here("data","raw-data","Electric_Vehicle_Population_Data.csv")
data <- read.csv(data_location)
output <- capture.output(str(data))
cat(output[1:3], sep="\n")
head(data)
summary(data)
colSums(is.na(data))
```
